---
title: "HealthCareAndCauseOfDeath.Rmd"
author: "Herbert Gutierrez, Ryan Wechter"
date: " October 16, 2015"
output: html_document
---

##Health Care Spending and Causes of Death by State
###CS329E: Project 3



####RStudio Configuration:
```{r}
sessionInfo()
```


##Loading our data from the Oracle Database
We modified the R script given to us to create a SQL code that would create the table in the Oracle Database.  We then loaded our data and could connect to the database to create our data frame in RStudio.
```{r}
source("../02 Data Wrangling/Project3_ETL.R", echo = TRUE)
```




##Graph 1: 
```{r}
source("../02 Data Wrangling/Graph1.R", echo = TRUE)
```

####Interpretation
This graph shows the ratio of the total number of dollars (1000's) spent by hospitals in each state to the number of cancer deaths in the state for the year 1999.  This ratio does not represent the average cost of a cancer patient to a hospital because the data excludes other types of death and does not account for other hospital expenses.  This graph is meant to illustrate the excessive over charging of patients for hospital care in the United States.  According to Beckers Hospital Review the average cost to a patient for a hospital stay in the United States is approximately $10,000 as compared to the cost to the hospital which ranges from as low as $500 in Florida to as high as $2000 in the District of Columbia.
  
  
##Graph 2:
```{r}
source("../02 Data Wrangling/Graph2.R", echo = TRUE)
```

####Interpretation
This graph shows the rising cost of healthcare in the state of Texas from 1999-2009.
  
  
##Graph 3:
```{r}
source("../02 Data Wrangling/Graph3.R", echo = TRUE)
```

####Interpretation
This graphs  
