---
title: "HealthCareAndCauseOfDeath.Rmd"
author: "Herbert Gutierrez, Ryan Wechter"
date: " October 16, 2015"
output: html_document
---

##Health Care Spending and Causes of Death by State
###CS329E: Project 3



####RStudio Configuration:
```{r}
sessionInfo()
```


##Loading our data from the Oracle Database
####Dataset 1: NHCE (FULL NAME)
We modified the R script given to us to create a SQL code that would create the table in the Oracle Database.  We then loaded our data and could connect to the database to create our data frame in RStudio.
```{r}
source("../02 Data Wrangling/Project3_ETL_Data1.R", echo = TRUE)
```


####Dataset 2: COD (FULL NAME)
```{r}
source("../02 Data Wrangling/Project3_ETL_Data2.R", echo = TRUE)
```


##Graph 1: INSERT TITLE HERE
```{r}
source("../02 Data Wrangling/Graph1.R", echo = TRUE)
```

####Interpretation
<<<<<<< HEAD
This Graph shows............... 
 
  
=======
This graph shows the ratio of the total number of dollars (1000's) spent by hospitals in each state to the number of cancer deaths in the state for the year 1999.  This ratio does not represent the average cost of a cancer patient to a hospital because the data excludes other types of death and does not account for other hospital expenses.  This graph is meant to illustrate the excessive over charging of patients for hospital care in the United States.  According to Beckers Hospital Review the average cost to a patient for a hospital stay in the United States is approximately $10,000 as compared to the cost to the hospital which ranges from as low as $500 in Florida to as high as $2000 in the District of Columbia.
>>>>>>> 1919d55c6a384041a5c585c9c2ef051a8449c6d5
  
  
##Graph 2: INSERT TITLE HERE
```{r}
source("../02 Data Wrangling/Graph2.R", echo = TRUE)
```

####Interpretation
<<<<<<< HEAD
This graph visualizes.............. 
  
 
=======
This graph shows the rising cost of healthcare in the state of Texas from 1999-2009.
>>>>>>> 1919d55c6a384041a5c585c9c2ef051a8449c6d5
  
  
##Graph 3: Suicide rates and prescription drugs grouped by state
```{r}
source("../02 Data Wrangling/Graph3.R", echo = TRUE)
```

####Interpretation
This graphs shows the relationship of prescription drug spending (by millions of dollars) for each state and the number of suicide deaths for each state. As you can see by the scatterplot, there is a positive correlation between suicide and the amount of prescription drug available according to the spending. We can therefore conclude that as more people in a population buy prescription drugs there is an increase in the suicide rates most likely due to the availability of such hard drugs.  
